---
title: "Systematic Review"
author: "Yamada Tarou"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
  word_document:
    toc: true
---

# Overview

This report summarizes a meta-analysis comparing mortality between **Group A** and **Group B**.

# Methods

## Statistical analysis

A meta-analysis was conducted using the **meta** package in R.  
For each study, the following 2×2 table was used:

- `event.e`: events in *Group A*
- `n.e`: total *Group A*
- `event.c`: events in *Group B*
- `n.c`: total *Group B*

The pooled effect size was estimated as an **odds ratio (OR)** using the Mantel–Haenszel method with both common-effect and random-effects models.  
A continuity correction of 0.5 was applied when necessary.

# Data and analysis

```{r setup, message=FALSE, warning=FALSE}
library(meta)
library(dplyr)
library(knitr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  dpi = 300
)
```

## Import data

```{r data}
# CSVファイル名は必要に応じて変更
dat <- read.csv("sample.csv", check.names = FALSE)

# 列名を統一
colnames(dat) <- c("study", "event.e", "n.e", "event.c", "n.c")

# 数値型に変換
dat$event.e <- as.numeric(dat$event.e)
dat$n.e     <- as.numeric(dat$n.e)
dat$event.c <- as.numeric(dat$event.c)
dat$n.c     <- as.numeric(dat$n.c)

kable(dat, caption = "Included studies")
```

## Meta-analysis

```{r meta}
exp_label  <- "Group A"
ctrl_label <- "Group B"

m <- metabin(
  event.e, n.e,
  event.c, n.c,
  data = dat,
  studlab = study,
  sm = "OR",
  method = "MH",
  random = TRUE,
  common = TRUE,
  incr = 0.5,
  allstudies = TRUE,
  method.random.ci = "HK"
)

m
```

## Pooled odds ratios

```{r pooled-results}
res_table <- data.frame(
  Model = c("Common effect", "Random effects"),
  OR = c(m$TE.common, m$TE.random),
  Lower = c(m$lower.common, m$lower.random),
  Upper = c(m$upper.common, m$upper.random)
) |>
  mutate(
    OR = exp(OR),
    Lower = exp(Lower),
    Upper = exp(Upper)
  )

kable(res_table, digits = 3, caption = "Pooled odds ratios")
```

## Heterogeneity

```{r heterogeneity}
heterogeneity <- data.frame(
  I2 = paste0(round(m$I2, 1), "%"),
  Tau2 = round(m$tau^2, 4),
  Q = round(m$Q, 3),
  p_value = signif(m$pval.Q, 3)
)

kable(heterogeneity, caption = "Heterogeneity statistics")
```

## Forest plot

```{r forestplot, fig.width=12, fig.height=7, out.width="100%"}
forest(
  m,
  comb.fixed = FALSE,
  comb.random = TRUE,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c("Study", "Events", "Total", "Events", "Total"),
  lab.e = exp_label,
  lab.c = ctrl_label,
  xlab = "Odds Ratio",
  xlim = c(0.1, 10),
  smlab = ""
)
```

# Interpretation

```{r interpretation, results='asis'}
or_random  <- exp(m$TE.random)
lcl_random <- exp(m$lower.random)
ucl_random <- exp(m$upper.random)
p_random   <- m$pval.random

cat("### Main finding\n\n")

cat(
  sprintf(
    "The pooled random-effects odds ratio for mortality was **%.2f** (95%% CI **%.2f to %.2f**)",
    or_random, lcl_random, ucl_random
  )
)

if (!is.na(p_random)) {
  cat(sprintf(", with a p-value of **%.3f**.\n\n", p_random))
} else {
  cat(".\n\n")
}

if (lcl_random > 1) {
  cat("This suggests that mortality was significantly higher in the **Candida auris** group.\n\n")
} else if (ucl_random < 1) {
  cat("This suggests that mortality was significantly lower in the **Candida auris** group.\n\n")
} else {
  cat("This suggests that there was **no statistically significant difference** in mortality between groups.\n\n")
}

cat(
  sprintf(
    "Statistical heterogeneity was **I² = %.1f%%**.",
    m$I2
  )
)

if (m$I2 < 25) {
  cat(" Heterogeneity was low.\n")
} else if (m$I2 < 50) {
  cat(" Heterogeneity was low to moderate.\n")
} else if (m$I2 < 75) {
  cat(" Heterogeneity was moderate to substantial.\n")
} else {
  cat(" Heterogeneity was substantial.\n")
}
```

# Session information

```{r sessioninfo}
sessionInfo()
```
